### 2014-04-03 Docs/unit_tests/unit_tests.tex
code references

In addition to the \maestro\ science problems, which use the full
capabilities of \maestro, there are a number of unit tests that
exercise only specific components of the \maestro\ solvers.  These
tests have their own drivers (a custom {\tt varden.f90}) that
initialize only the data needed for the specific test and call
specific \maestro\ routines directly.

@@

  This test initializes a 1D radial base state quantity with a
  Gaussian distribution, maps it into the 3D domain (assuming a
  spherical geometry) using the routines provided by the {\tt
    fill\_3d\_module} module, and then calls {\tt average} to put it
  back onto a 1D radial array.  This way we test the accuracy of our
  procedure to map between the 1D radial and 3D Cartesian states.
  The output from this test was described in detail in
  \cite{multilevel}.

@@

  This simply tests the reaction network by calling the \maestro\ {\tt
  react\_state} routine directly.  The network is selected in the {\tt
  GNUmakefile} by setting the {\tt NETWORK\_DIR} variable.  A 3d cube
  is setup with density varying on one axis, temperature varying on
  another, and the composition varying on the third.  The density and
  temperature ranges are set in the inputs file.  The composition is
  read in via an input file.

>>>>

In addition to the \maestro\ science problems, which use the full
capabilities of \maestro, there are a number of unit tests that
exercise only specific components of the \maestro\ solvers.  These
tests have their own drivers (a custom \code{varden.f90}) that
initialize only the data needed for the specific test and call
specific \maestro\ routines directly.

@@

  This test initializes a 1D radial base state quantity with a
  Gaussian distribution, maps it into the 3D domain (assuming a
  spherical geometry) using the routines provided by
  the \code{fill\_3d\_module} module, and then calls \code{average} to
  put it back onto a 1D radial array.  This way we test the accuracy
  of our procedure to map between the 1D radial and 3D Cartesian
  states.  The output from this test was described in detail
  in \cite{multilevel}.

@@

  This simply tests the reaction network by calling
  the \maestro\ \code{react\_state} routine directly.  The network is
  selected in the {\tt GNUmakefile} by setting the {\tt NETWORK\_DIR}
  variable.  A 3d cube is setup with density varying on one axis,
  temperature varying on another, and the composition varying on the
  third.  The density and temperature ranges are set in the inputs
  file.  The composition is read in via an input file.
